\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[top=1.5cm, bottom=1.5cm, scale=0.8]{geometry}

% personal data
\name{Jacobus}{Lock}
%\title{Ambitious engineer seeking new, exciting opportunities}
\address{}{Lincoln, UK}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44 (0)7449 739341}                   % optional, remove / comment the line if not wanted
\email{jaycee.lock@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{jclock.co.uk}                         % optional, remove / comment the line if not wanted
\social[linkedin][linkedin.com/in/jacobus-lock/]{jacobus-lock}
\social[github][github.com/jayceelock]{jayceelock}                         % optional, remove / comment the line if not wanted
\social[twitter][twitter.com/JayceeLock]{jayceelock}
%\social[scholar][scholar.google.com/citations?user=MLYdvnwAAAAJ]{JC Lock}

\begin{document}
\makecvtitle

\section{Education}

\cventry{2016 -- 2020}{Doctor of Computer Science (PhD)}{University of Lincoln}{Lincoln}{UK}{My thesis investigated the feasibility of applying active vision techniques to human activities. This was done by combining machine learning, human-machine interfacing and computer vision in a novel way to produce an indoor navigation system for the visually impaired which can guide a person to a target object that is placed in an unknown location. Project website: lcas.github.io/ActiVis. Thesis: tinyurl.com/ylyyx4je}%{Focus on computer vision, human-machine interfacing, machine learning and assistive technologies}
\cventry{2014 -- 2015}{Master of Mechatronic Engineering (M.Eng)}{Stellenbosch University}{Stellenbosch}{South Africa}{My thesis consisted of making a method to determine the pose accuracy of a drone in flight in the outdoors with computer vision and machine learning regression techniques. The resulting error results were integrated into a drone's control model to enable more accurate control in a heliostat mirror field. Report available at: bit.ly/2wjp7q0}%{Focus on UAV control, machine learning and computer vision}
\cventry{2010 -- 2013}{Bachelor of Mechatronic Engineering (B.Eng)}{Stellenbosch University}{Stellenbosch}{South Africa}{}  % Arguments not required can be left empty
 
\section{Work Experience}

\cventry{2020 -- Present}{Post-Doctoral Research Fellow}{University of Lincoln}{Lincoln}{UK}{PDRA for the LASERBOOM project. Responsible for mounting and collecting LIDAR, IMU and GNSS data to be used in an agriculture robot for localisation and spray-boom control. Also built a model to estimate the shape of a crop canopy with LIDAR data to enable the spray boom to avoid hitting and damaging the crop. }
\cventry{2020}{Robotics Engineer}{SAGA Robotics Ltd.}{Lincoln}{UK}{Worked as an engineer on SAGA's autonomous agriculture robot platform (`Thorvald'). My duties included building a simulation environment for an autonomous strawberry picker using the ROS framework. }
\cventry{2019 -- 2020}{Research Assistant}{University of Lincoln}{Lincoln}{UK}{RA for the NCNR project which is looking into integrating autonomous robots in a nuclear power plant. My responsibilities included mounting robotic arms on a mobile platform and building a simulation model for the resulting system. }

\section{Personal Projects}

\cvitem{Home Server}{Building a home server with leftover PC parts to host my web services (Git, webpage, etc.) and store all my data and records. }
\cvitem{Biltong Dryer}{Making a dryer I can use to make biltong (delicious South African snack). An Arduino controls a fan and heat element to regulate the box's climate so that you can better control the biltong's dryness and taste.}
\cvitem{NFCPay}{Designed and implemented a cashless vending machine that allows purchases to be made using QR codes, NFC or student ID authentication, and deployed a server to track and encrypt all transactions. }
\cvitem{EchoLocate}{Developed a proof-of-concept geo-tracker app that listens to the environment for ultrasonic trigger cues and logs the geo-location once such a cue is detected. }
\cvitem{PiLock}{Created a centralised lock control system where a user can control the status of a group of locks with a Android phone and uses a back-end server for authentication and user logging. }
\cvitem{TrainTown}{Built a Raspberry Pi-based controller for a model town-train system. Everything is controlled via a remote web interface. }

\section{Technical Skills}

\cvitem{Strong}{Android, Java, C\textbackslash C++, Python, Git, Matlab, Latex, Linux} 
\cvitem{Knowledgeable}{Django, Kotlin, Bash, embedded systems, Rust, web hosting, Docker} 

\section{Languages}

\cvitem{Afrikaans}{Native}
\cvitem{English}{Native, raised in bilingual household}
\cvitem{German}{Basic, learning}

\section{Hobbies and Interests}

\cvitem{}{Travelling, history, development economics, outdoor exercise, reading, cooking}

\section{References}

\begin{cvcolumns}
  \cvcolumn{Dr. Charles Fox}
  {
    \begin{itemize}
      \item Post-doctorate supervisor
      \item \url{chfox@lincoln.ac.uk}
    \end{itemize}
  }
  \cvcolumn{Halvard Grimstad}
  {
    \begin{itemize}
      \item SAGA Robotics Manager
      \item \url{hgrimstad@sagarobotics.com}
    \end{itemize}
  }
  \cvcolumn{Dr. Grzegorz Cielniak}
  {
    \begin{itemize}
      \item Research assistant supervisor
      \item \url{gcielniak@lincoln.ac.uk}
    \end{itemize}
  }
\end{cvcolumns}

\cvitem{}{More available upon request}

\end{document}end 
